# Instructor Guide {-}

## Lesson Plan  {-}

Coming soon!

## Notes for Instructors {-}

This R-based activity can be run on a different platform, such as your own personal installation of [R](https://www.r-project.org/) or [Posit](https://posit.co/)(formerly called RStudio), depending on your needs. 

More Coming soon!

## Setting up Billing on AnVIL {-}

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "04_Billing.Rmd",
  repo_name = "jhudsl/AnVIL_Book_Instructor_Guide"
)
```

## Setting up the Class Activity {-}

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "05_Class_setup.Rmd",
  repo_name = "jhudsl/AnVIL_Book_Instructor_Guide"
)
```

## Checklist for Running the Activity on AnVIL {-}

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "06_Running_the_class.Rmd",
  repo_name = "jhudsl/AnVIL_Book_Instructor_Guide"
)
```

## Getting Credit for Professional Development {-}

We are happy to provide a letter to your supervisor, department head, or dean to indicate you've worked through this content and intend to use it in your class.