This activity is based on work published by Drs. Elizabeth Carlen and Jason Munshi-South in 2021, "Widespread genetic connectivity of feral pigeons across the Northeastern megacity". In this module, you will work with SNP data from a subsample of 50 feral pigeons (collected in 6 different Northeastern US cities) that were captured and sampled in Carlen and Munshi-South's study. You will calculate PCA and create plots to visualize the population structure among these pigeons using the R programming language.

You can read the full study [here](https://onlinelibrary.wiley.com/doi/epdf/10.1111/eva.12972).

## Introduction

This is a brief video introduction to the activity.

You can view and download the Google Slides [here](https://docs.google.com/presentation/d/1meLiZzX1TSPvSOMwOSXUX9FyM82fZk1iqGpF3j6PsNM/edit#slide=id.p)

## Before you begin

You will need to create a Google account in order to use AnVIL.

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_google_create_account.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```

You will also need to clone the AnVIL workspace for this activity.

# RStudio

This activity uses the RStudio environment on AnVIL.

## Video overview on using RStudio

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_rstudio_video.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```

## Launching RStudio

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_rstudio_launch.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```

## Touring RStudio

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_rstudio_tour.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```

## Pausing RStudio

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_rstudio_pause.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```


## Deleting RStudio


```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_rstudio_delete.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```